### 2014-06-04 writing/S'14 paper/quantifiers.tex
Proofed sec. 5

Our data consists of pairs of sentences generated from a small
artificial grammar. Each sentence contains a quantifier, a noun, which
may be negated, and an intransitive verb which may be negated. We use
the basic quantifiers \ii{some}, \ii{most}, \ii{all}, \ii{two}, and
\ii{three}, and each of their duals over negation \ii{no},
\ii{not-all}, \ii{not-most}, \ii{less-than-two}, and
\ii{less-than-three}. We also include five nouns, four intransitive
verbs, and the negation symbol \ii{not}. In order to be able to define
relations between sentences with differing lexical items, we define
the lexical relations between each noun--noun pair, each verb--verb
pair, and each quantifier--quantifier pair. The grammar accepts
aligned pairs of sentences of this form and calculates the natural
logic relationship between them.  Some examples of these data are
provided in Table~\ref{examplesofdata}.  As in previous sections, the
goal of learning is then to assign these relational labels accurately
on unseen cases.

@@

We evaluate the model using two experimental settings. In the simpler
setting, we randomly sample 85\% of the data and evaluate on the
remaining 15\%. In this setting, the model is being asked to learn a
complete reasoning system for the limited language and logic presented
in the training data, but it is not being asked to generalize to test
examples that are substantially different from those it was trained
on. Crucially though, to succeed on this task, the model must be able
to recognize all of the lexical relations between the nouns, verbs,
and quantifiers and how they interact. For instance, it might see
\eqref{p1} and \eqref{p2} in training and, from that information,
determine \eqref{p3}.
%
\begin{gather}
  \text{(most turtle) swim} \natalt \text{(no turtle) move}\label{p1}
  \\
  \text{(all lizard) reptile} \natrev  \text{(some lizard) animal}\label{p2}
  \\
  \text{(most turtle) reptile} \natalt \text{(no turtle) animal}\label{p3}
\end{gather}

@@

\begin{table}[htp]
  \centering
  \begin{tabular}{ l rrr }
    \toprule
    Data & Most frequent class & TODO dim RNN (\%) & 16 dim RNTN (\%)\\
    \midrule
    \textsc{all split}	& 35.4 &	TODO&	88.1 
    \\[1ex]    
    \textsc{pair two/less-than-two}	& 59.8 &	TODO &	92.4 \\
    \textsc{pair not-all/not-most}	&0 &	   TODO  &	82.1 \\
    \textsc{pair all/some}	& 0& TODO  &	80.4 \\
    \textsc{pair no/no}	& 30.8 &	TODO &	100 \\
    \bottomrule
  \end{tabular}
  \caption{Quantifier experiment performance. 
    Most frequent class accuracy is measured against the most frequent class in the training data, $\natind$.}
  \label{resultstable}
\end{table}

>>>>

Our data consists of pairs of sentences generated from a small
artificial grammar. Each sentence contains a quantifier, a noun which
may be negated, and an intransitive verb which may be negated. We use
the basic quantifiers \ii{some}, \ii{most}, \ii{all}, \ii{two}, and
\ii{three}, and their negations \ii{no},
\ii{not-all}, \ii{not-most}, \ii{less-than-two}, and
\ii{less-than-three}. We also include five nouns, four intransitive
verbs, and the negation symbol \ii{not}. In order to be able to define
relations between sentences with differing lexical items, we define
the lexical relations between each noun--noun pair, each verb--verb
pair, and each quantifier--quantifier pair. The grammar accepts
aligned pairs of sentences of this form and calculates the natural
logic relationship between them.  Some examples of these data are
provided in Table~\ref{examplesofdata}.  As in previous sections, the
goal of learning is then to assign these relational labels accurately
to unseen pairs of sentences.

@@

We evaluate the model using two experimental settings. In the simpler
setting, \textsc{all split}, we randomly sample 85\% of the data and evaluate on the
remaining 15\%. In this setting, the model is being asked to learn a
complete reasoning system for the limited language and logic presented
in the training data, but it is not being asked to generalize to test
examples that are substantially different from those it was trained
on. Crucially though, to succeed on this task, the model must be able
to recognize all of the lexical relations between the nouns, verbs,
and quantifiers and how they interact. For instance, it might see
\eqref{p1} and \eqref{p2} in training and, from that information,
determine \eqref{p3}.
%
\begin{gather}
  \text{(most turtle) swim} \natalt \text{(no turtle) move}\label{p1}
  \\
  \text{(all lizard) reptile} \natrev  \text{(some lizard) animal}\label{p2}
  \\
  \text{(most turtle) reptile} \natalt \text{(no turtle) animal}\label{p3}
\end{gather}

@@

\begin{table}[htp]
  \centering
  \begin{tabular}{ l rrr }
    \toprule
    Data & Most frequent class & TODO dim RNN (\%) & 16 dim RNTN (\%)\\
    \midrule
    \textsc{all split}	& 35.4 &	60.4&	94.4
    \\[1ex]    
    \textsc{pair two/less-than-two}	& 59.8 &	76.4 &	97.1 \\
    \textsc{pair not-all/not-most}	&0 &	   65.6  &	79.2 \\
    \textsc{pair all/some}	& 0& 60.7  &	79.5 \\
    \textsc{pair no/no}	& 30.8 &	65.8 &	100 \\
    \bottomrule
  \end{tabular}
  \caption{Quantifier experiment performance. 
    Most frequent class accuracy is measured against the most frequent class in the training data, $\natind$.}
  \label{resultstable}
\end{table}
